An exact Riemann solver for one-dimensional multi-material elastic-plastic flows with Mie-Gr\"uneisen equation of state without vaccum

### 2019-07-12 Manuscript20190712.tex
111

\title{An exact Riemann solver for one-dimensional multi-material elastic-plastic flows with Mie-Gr\"uneisen equation of state}
\author{Li Liu$^1$, Jun-bo Cheng $^{1,*}$}
%\author{Li Liu$^1$, Jun-bo Cheng $^{1,*}$, Jiequan Li $^{1}$}
%\cortext[mycorrespondingauthor]{
%Correspondence to: Junbo Cheng, Institute of Applied Physics and Computational Mathematics, Beijing 100094, China. E-mail: Cheng\_junbo@iapcm.ac.cn}

@@

\begin{abstract}
  In this paper, we present exact Riemann solvers for the Riemann problem and the half Riemann problem, respectively,  for one-dimensional multi-material elastic-plastic flows with the Mie-Gr\"uneisen equation of state(EOS), hypo-elastic constitutive model and  the von Mises' yielding condition. We first analyze the Jacobian matrixes in  both elastic and plastic states, and then build relations between different variables across different type of waves. Based on these formulations, an exact Riemann solver is constructed with totally thirty-six possible cases of wave structures. Although Gao and Liu\cite{gao20171d} also developed the exact Riemann solver for 1D elastic plastic flows, but the EOS they used is very simple. Moreover, the exact Riemann solver developed by them may result in wrong solutions when the initial material is in the plastic state, which has been proven in one of our tests. Comparing with the exact Riemann solver developed by Gao and Liu, our exact Riemann solver uses a more complex EOS and overcomes these mistakes. A large number of tests prove the rightness of our exact Riemann solver. Moreover, an exact Riemann solver is also deduced for the half Riemann problem and  its validity is tested  by two examples. 
\end{abstract}

@@

In the development history of hydrodynamic numerical methods, the exact Riemann solver has played a very important role as it not only can give a guide and reference to the construction of approximate Riemann solvers, but also can be used to determine the convergence and stability of numerical schemes. However, building the exact Riemann solver for 1D elastic-plastic flows is not that easy. Comparing with the governing equations system of 1D pure fluids, for 1D elastic-plastic flows, there are two more equations: a non-conservative constitutive equation and the von Mises yielding condition.  The non-conservative character of the constitutive equation increases the difficulty in constructing  Riemann solvers, while the von Mises yielding condition may lead to more non-linear waves in the wave structure of Riemann solvers. Moreover, in a general way, the equation of state(EOS) for solid materials is more complex than that for pure fluids, which directly increases the difficulty in solving the Riemann problem.

For the elastic-plastic flow with the hypo-elastic constitutive model and  the von Mises' yielding condition,  some approximate Riemann solvers\cite{gavrilyuk2008modelling,cheng2015high,cheng2016harten,liumulti} have been developed recently. However, for the exact Riemann solver, the research is relatively few, and focuses mainly on the problem with relatively simple constitutive models and relatively simple EOSs.
%them are only considered with  simple constitutive models and simple EOSs.
For example, Garaizar \cite{garaizar1991solution} and Miller \cite{miller2004iterative} introduced  an exact Riemann solver for elastic or hyper-elastic materials, Gao and Liu \cite{gao20171d,gao2018complete} firstly considered the yielding effect and developed an exact elastic-perfectly plastic solid Riemann solver. But there are two shortcomings in their works. Firstly, the EOS used by them is very simple: in the elastic state, the material derivative of pressure is the linear function of the strain rate, which means the energy equation is not necessary in the elastic state; in the plastic state,  a linear  "stiffened-gas" EOS was used. { \color{red} Secondly,  unloading (for example, an expanding process to a compressed yielding material) and reloading processes are not considered in the construction  of their Riemann solvers. This may leads to wrong solutions as the unloading and reloading are very common in the real computing cases, shown in our $5$th numerical example. }
In fact, according to the relations in the governing equations, even if the initial material reaches the elastic limit and in a plastic state, after an unloading process, the material may change back to an elastic state and then may re-change to a plastic state by a reloading process.

@@

%For example, Garaizar \cite{garaizar1991solution} designed an exact Riemann solution of isotropic hyperelastic material theoretically.  Miller \cite{miller2004iterative} presented a general iterative method for the solution of the Riemann problem for hyperbolic elastic systems. Gao and Liu \cite{gao20171d,gao2018complete} firstly considered the yielding condition in, and proposed an exact elastic-perfectly plastic solid Riemann solver with both elastic and plastic states. As many as thirty-six \cite{gao20171d} and sixty-four \cite{gao2018complete} different solution types are considered in their works. However, in their papers,  a linear  "stiffened-gas" EOS was used in the plastic state and a more simple linear relation of pressure and strain rate is used in the elastic state. This simplification can truly deduce to simple relations  across the shock wave and rarefaction wave, but we still need an exact Riemann solver with a uniform and more common used EOS and equations system for different elastic-plastic materials.

In this paper, we want to construct an exact Riemann solver for the system of 1D elastic-plastic flows with the Mie-Gr\"uneisen EOS, the hypo-elastic constitutive model and the von Mises' yielding condition. As every knows, the Mie-Gr\"uneisen EOS is complex and is used widely  in many engineering problems, which makes the energy equation must be included in the system of elastic-plastic flows and so we have to use some special methods to resolve the rarefaction wave. Otherwise, we analyse the Jacobian matrix and find, in the wave structures of Riemann solvers, there may be three to five waves, including one contact wave and other two to four non-linear waves. These nonlinear waves may be elastic shock waves, elastic rarefaction waves,  plastic shock waves or plastic rarefaction waves. Moreover, elastic wave always runs faster than the followed plastic wave. So there are thirty-six possible cases of the wave structures in the Riemann solver.  Besides, both the changing from elastic to plastic (loading or reloading) and  the converse changing from plastic to elastic(unloading)  are considered in the Riemann problem.
%For a given case, we will obtain theoretical relations of all the states as functions of density. At last,  through an iteration process of densities at both sides of the contact wave, the  exact solution will be obtained. Also, the half Riemann problem and its exact solution are considered in this paper.

@@

The above equations are just for the elastic status of the solid material.
If the materials are in the plastic state, the above equations can be simplified
and the jacobian matrix and sonic velocity are different,  correspondingly.
We will discuss them separately.
\subsection{Elastic state}
\subsubsection{Jacobian matrix in elastic regions} %and the eigenvalues and eigenvectors}
For the Mie-Gr\"uneisen EOS, if the material is not yielding,
\begin{equation}
  |s_{xx}| < \frac{2}{3}Y_0,
\end{equation}
the system (\ref{eq:1d}) can be written as
\begin{equation}
 \partial_t \mathbf{Q} +\mathbf{J}_{e}(\mathbf{{Q}})\partial_x\mathbf{Q} = 0,
\end{equation}
where $Q = (\rho, \rho u, \rho E, s_{xx})$, and the Jacobian matrix is
\begin{equation}\label{eq:Jcb}
  \mathbf{J}_{e}(Q) = \left[\begin{array}{llll}
      0 & 1 & 0 & 0 \\
      -u^2 + \frac{\partial p}{\partial \rho} +\Gamma(\frac{u^2}{2}-e)& u(2-\Gamma)& \Gamma & -1 \\
	  (\Gamma(\frac{u^2}{2}-e)-e-\frac{u^2}{2}+\frac{\sigma}{\rho}+\frac{\partial p}{\partial \rho})u & -\Gamma u^2 -\frac{\sigma}{\rho}+\frac{u^2}{2} +e & (1+\Gamma)u& -u\\
    \frac{4}{3}\mu\frac{u}{\rho} & -\frac{4}{3}\mu\frac{1}{\rho}& 0 & u \\
\end{array}
\right],
\end{equation}
where $\Gamma = \frac{\Gamma_0\rho_0}{\rho} $.

@@

\subsubsection{A relation between $\rho$ and $s_{xx}$ }

Thanks to (\ref{eq:mt}), equations of the density and the deviatoric stress in Eq.(\ref{eq:1d}) can be written as
  \begin{equation}\label{eq:d1}
    \frac{\partial u}{\partial x} = -\frac{1}{\rho}\frac{d\rho}{dt},
  \end{equation}
  and
  \begin{equation}\label{eq:s1}
    \frac{ds_{xx}}{dt}=\frac{4}{3}\mu\frac{\partial u}{\partial x}.
  \end{equation}

  Substituting (\ref{eq:d1}) into (\ref{eq:s1}) yields
%  We can get a relation of density and deviatoric stress,
  \begin{equation}
    \frac{ds_{xx}}{dt}=-\frac{4}{3}\mu \frac{1}{\rho}\frac{d\rho}{dt}.
\end{equation}
Integrating the above equation from the data in front of a wave to the data behind the wave and performing some simple algebraic manipulations, one can get
\begin{equation}\label{eq:rhosxx}
  s_{xx}+\frac{4}{3}\mu\text{ln}(\rho) = \text{constant}
\end{equation}
This relation always hold in the elastic state.

@@

@@

\noindent
\textbf{Iterations begin:}
\begin{enumerate}[Step 1]
  \item Determining the case of the wave structure:

	Given $\rho _{L(k)}^*$ and  $\rho _{R(k)}^*$ in the $k$-th  iteration step, we can use the method introduced in Section \ref{sec:deter} to determine the case of wave structure of this Riemann problem. In the  procedure for solving the  Riemann problem, the subscript $(k)$ means the variable in the $k$-th  iteration step.

@@

  After determining the structure case, we need  to solve  Cauchy stresses and velocities in regions $\mathbf{Q}^*_L$ and $\mathbf{Q}^*_R$, those are given in Section \ref{sec:functions}.

@@

Combining (\ref{shock1}) and (\ref{yield1}), we can find, in any side of the wave structure of this Riemann problem, there are six cases showed in Table \ref{tab:cases}, where capital letters ``$S$'' and ``$R$'' mean the shock and rarefaction wave, respectively; superscript letters ``$E$'' and  ``$P$'' indicate the elastic or plastic state of a wave, respectively. Otherwise, the  subscript $L$ or  $R$  are omitted for simplification.

@@

For shock waves cases, the  deviatoric stresses in $\mathbf{Q}_{L}^*$  and  $\mathbf{Q}_{R}^*$ are given as
\begin{equation}
s_{xx}(\rho) = \left\{\begin{aligned}
	  & -\frac{4}{3}\mu\text{ln}\left(\frac{\rho}{\tilde{\rho}_{L(R)}}\right)+\tilde{s}_{xxL(R)},
	\quad  &\text{case ($S^E$)},\\
	& -\frac{2}{3}Y_0,   \quad
	&\text{cases ( $S^P$ and $S^ES^P$)}.
  \end{aligned} \right.
  \end{equation}
(\ref{eq:shocke}) gives direct expressions for the
By the equation of (\ref{eq:shocke}), the pressure is given as
\begin{equation}
  p_{L(R)}^*=
  \frac{2t\left(c_1f(\rho_{L(R)}^*/\rho_0)+\tilde{e}_{L(R)}\right)-\left(\tilde{\sigma}_{L(R)}+{s}_{xx}(\rho_{L(R)}^*)\right)}{2tc_0-1},
\end{equation}
where $c_0 = \frac{1}{\rho_0\Gamma_0}$, $c_1 = \frac{a_0^2}{\Gamma_0}$ and $ t=\frac{\rho^*_{L(R)} \tilde{\rho}_{L(R)}}{\rho^*_{L(R)}- \tilde{\rho}_{L(R)}}$.

@@

	The initial density is  given as
\begin{equation}
\rho_{(1)}^* = \rho_R.
\end{equation}
\textbf{Iterations begin:}
\begin{enumerate}[Step 1]
  \item Determine the case of the wave structure:

	Given the value of  $\rho _{(k)}^*$ in the $k$-th iteration step, use the methods introduced in Section \ref{sec:deter} to determine the case of wave structure of this Riemann problem. Here the subscript $(k)$ means the variable in the $k$-th  iteration step.

@@

	After determining the structure case, evaluate the velocity ( or  the Cauchy stress) in  the region $\mathbf{Q}^*$ and the details are given in Section \ref{sec:functions}.

@@

\subsection{Test 1}
In this case, the material is yielding at both sides, so the solution structure has three waves with two plastic shock waves and one contact.
The initial condition is
\begin{equation}
 \left\{ \begin{aligned}
&	 \text{L: Al,}\quad  \rho = 2785 \text{kg}/\text{m}^3, \quad  u = 20\text{m}/\text{s}, \quad  p = 1.0\text{Pa}, \quad  s_{xx}=-2.0\times 10^8 \text{Pa},\\
&	 \text{R: Al,}\quad  \rho = 2785 \text{kg}/\text{m}^3, \quad  u = 0\text{m}/\text{s}, \quad  p = 1.0\text{Pa}, \quad  s_{xx}=-2.0\times 10^8 \text{Pa},\\
   \end{aligned}
 \right.
\end{equation}
It can be seen that the exact solution matches the numerical results very well in Fig.\ref{fig:case1}.
\begin{figure}[ht]
  \centering

@@

    \caption{Comparison results for Test 1 with the structure of $S^P|S^P$.  }
  \label{fig:case1}
\end{figure}
\subsection{Test 2}
Here we consider a case with yielding process at both sides, so there are five waves in the wave structure of this Riemann problem. The initial condition is
\begin{equation}
 \left\{ \begin{aligned}
	 &	 \text{L: Al,}\quad  \rho = 2785 \text{kg}/\text{m}^3, \quad  u = 800\text{m}/\text{s}, \quad  p = 1.0\text{Pa}, \quad  s_{xx}=0.0 \text{Pa},\\
&	 \text{R: Al,}\quad  \rho = 2785 \text{kg}/\text{m}^3, \quad  u = 0\text{m}/\text{s}, \quad  p = 1.0\text{Pa}, \quad  s_{xx}=0.0 \text{Pa},\\
   \end{aligned}
 \right.
\end{equation}
Shown in Fig.\ref{fig:case2}, the exact solution matches the numerical results well generally, except the under-cooling effect performed in the numerical results, but it is not considered in the designing of the exact Riemann solver.
\begin{figure}[ht]
  \centering
  \includegraphics[width= 7cm] {case2rho.pdf}
  \includegraphics[width= 7cm] {case2u.pdf}
  \includegraphics[width= 7cm] {case2p.pdf}
  \includegraphics[width= 7cm] {case2sxx.pdf}
  \caption{Comparison results for Test 2 with the structure of $S^ES^P|S^PS^E$.  }
  \label{fig:case2}
\end{figure}

\subsection{Test 3}
In this example, we test the case with two elastic rarefaction waves. In the wave structure there is one elastic rarefaction wave on each side of the contace wave. The initial condition is given as
\begin{equation}
 \left\{ \begin{aligned}
	 &	 \text{L: Al,}\quad  \rho = 2785 \text{kg}/\text{m}^3, \quad  u = -2.0\text{m}/\text{s}, \quad  p = 1.0\time 10^7\text{Pa}, \quad  s_{xx}=0.0 \text{Pa},\\
	 &	 \text{R: Al,}\quad  \rho = 2785 \text{kg}/\text{m}^3, \quad  u = 2.0\text{m}/\text{s}, \quad  p = 1.0\times 10^7 \text{Pa}, \quad  s_{xx}=0.0 \text{Pa},\\
   \end{aligned}
 \right.
\end{equation}
We can see that the results of the exact solution match the numerical results very well.
%
%j\section*{Conclusions}
\begin{figure}{ht}
  \centering

@@

    \caption{Comparison resutls for Test 6 with the structrures of $R^P|R^PR^E$.  }
  \label{fig:case5}
\end{figure}
\subsection{Test 7}
In this test, we consider an example with zero initial velocities on both sides, driving by the gradient of the pressure, there are rarefaction waves produced into the higher pressure side and shock waves generated into the lower pressure side. The initial condition is given as
\begin{equation}
 \left\{ \begin{aligned}
	 &	 \text{L: Al,}\quad  \rho = 2785 \text{kg}/\text{m}^3, \quad  u = 0.0\text{m}/\text{s}, \quad  p = 1.0\times 10^{10} \text{Pa}, \quad s_{xx}= 0.0 \text{Pa},\\
	 &	 \text{R: Al,}\quad  \rho = 2785 \text{kg}/\text{m}^3, \quad  u = 0.0\text{m}/\text{s}, \quad  p = 1.0 \times 10^2 \text{Pa}, \quad  s_{xx}=0.0\text{Pa}.\\
   \end{aligned}
 \right.
\end{equation}
Shown in Fig.\ref{fig:case9}, we can see there are two shocks in the right side and two rarefaction waves on the left side.
\begin{figure}[ht]
  \centering

>>>>

\title{An exact Riemann solver for one-dimensional multi-material elastic-plastic flows with Mie-Gr\"uneisen equation of state without vaccum}
\author{Li Liu$^1$, Jun-bo Cheng $^{1,*}$}
%\author{Li Liu$^1$, Jun-bo Cheng $^{1,*}$, Jiequan Li $^{1}$}
%\cortext[mycorrespondingauthor]{
%Correspondence to: Junbo Cheng, Institute of Applied Physics and Computational Mathematics, Beijing 100094, China. E-mail: Cheng\_junbo@iapcm.ac.cn}

@@

\begin{abstract}

  In this paper, we present exact Riemann solvers for the Riemann problem and the half Riemann problem, respectively,  for one-dimensional multi-material elastic-plastic flows with the Mie-Gr\"uneisen equation of state(EOS), hypo-elastic constitutive model and  the von Mises' yielding condition. We first  analyze the Jacobian matrixes in  both elastic and plastic states, and then build relations between different variables across different type of waves. Based on these formulations, an exact Riemann solver is constructed with totally thirty-six possible cases of wave structures. {\color{red} In our work,  a four-equation Eulerian hyperbolic governing system is used and the elastic and plastic states are controlled by uniform equations and same EOS. The transformations of elastic and plastic states are  determined by the deviatoric stress spontaneously}. A large number of tests prove the rightness of our exact Riemann solver. Moreover, an exact Riemann solver is also deduced for the half Riemann problem and  its validity is tested  by two examples. 
\end{abstract}

@@

In the development history of hydrodynamic numerical methods, the exact Riemann solver has played a very important role as it not only can give a guide and reference to the construction of approximate Riemann solvers, but also can be used to determine the convergence and stability of numerical schemes. However, building the exact Riemann solver for 1D elastic-plastic flows is not that easy. Comparing with the governing equations system of 1D pure fluids, for 1D elastic-plastic flows, there are two more equations: a non-conservative constitutive equation and the von Mises yielding condition.  The non-conservative character of the constitutive equation increases the difficulty in constructing  Riemann solvers, while the von Mises yielding condition may lead to more non-linear waves in the wave structures of Riemann solvers. Moreover, in a general way, the equation of state(EOS) for solid materials is more complex than that for pure fluids, which directly increases the difficulty in solving the Riemann problem.

For the elastic-plastic flow with the hypo-elastic constitutive model and  the von Mises' yielding condition,  some approximate Riemann solvers\cite{gavrilyuk2008modelling,cheng2015high,cheng2016harten,liumulti} have been developed recently. However, for the exact Riemann solver, the research is relatively few, and focuses mainly on the problem with relatively simple constitutive models and relatively simple EOSs.
%them are only considered with  simple constitutive models and simple EOSs.
For example, Garaizar \cite{garaizar1991solution} and Miller \cite{miller2004iterative} introduced  an exact Riemann solver for elastic or hyper-elastic materials, Gao and Liu \cite{gao20171d,gao2018complete} firstly considered the yielding effect and developed an exact elastic-perfectly plastic solid Riemann solver. {\color{red} In their works, a five-equation Eulerian governing system is constructed and a complete list of sixty-four cases of wave type is presented.     }

@@

%For example, Garaizar \cite{garaizar1991solution} designed an exact Riemann solution of isotropic hyperelastic material theoretically.  Miller \cite{miller2004iterative} presented a general iterative method for the solution of the Riemann problem for hyperbolic elastic systems. Gao and Liu \cite{gao20171d,gao2018complete} firstly considered the yielding condition in, and proposed an exact elastic-perfectly plastic solid Riemann solver with both elastic and plastic states. As many as thirty-six \cite{gao20171d} and sixty-four \cite{gao2018complete} different solution types are considered in their works. However, in their papers,  a linear  "stiffened-gas" EOS was used in the plastic state and a more simple linear relation of pressure and strain rate is used in the elastic state. This simplification can truly deduce to simple relations  across the shock wave and rarefaction wave, but we still need an exact Riemann solver with a uniform and more common used EOS and equations system for different elastic-plastic materials.
{\color{red}
 Enlighen by but different from the works of Gao and Liu \cite{gao20171d,gao2018complete},
 in this paper, we want to construct an exact Riemann solver for the system of 1D elastic-plastic flows with the Mie-Gr\"uneisen EOS, the hypo-elastic constitutive model and the von Mises' yielding condition. Firstly, the elastic and plastic states are controlled by same equations but only different in the deviatoric stress, so there are  four equations in the governing system. Secondly, the same Mie-Gr\"uneisen EOS is used in both the elastic and plastic states.  As every knows, the Mie-Gr\"uneisen EOS is complex and is used widely in many engineering problems, which makes the energy equation must be included in the system of elastic-plastic flows and so we have to use some special methods to resolve the rarefaction wave.  Otherwise, we analyse the Jacobian matrix and find, in the wave structures of Riemann solvers, there may be three to five waves, including one contact wave and other two to four non-linear waves. These nonlinear waves may be elastic shock waves, elastic rarefaction waves,  plastic shock waves or plastic rarefaction waves. Moreover, elastic waves always runs faster than the followed plastic wave. So there are thirty-six possible cases of the wave structures in the Riemann solver.  Besides, both the changing from elastic to plastic and  the converse changing from plastic to elastic  are considered in the Riemann problem.}
%For a given case, we will obtain theoretical relations of all the states as functions of density. At last,  through an iteration process of densities at both sides of the contact wave, the  exact solution will be obtained. Also, the half Riemann problem and its exact solution are considered in this paper.

@@

The above equations are just for the elastic status of the solid material.
If the material is in the plastic state, the above equations can be simplified
and the jacobian matrix and sonic velocity are different,  correspondingly.
We will discuss them separately.
\subsection{Elastic state}
\subsubsection{Jacobian matrix in elastic regions} %and the eigenvalues and eigenvectors}
For the Mie-Gr\"uneisen EOS, if the material is not yielding,
\begin{equation}
  |s_{xx}| < \frac{2}{3}Y_0,
\end{equation}
the system (\ref{eq:1d}) can be written as
\begin{equation}
 \partial_t \mathbf{Q} +\mathbf{J}_{e}(\mathbf{{Q}})\partial_x\mathbf{Q} = 0,
\end{equation}
where $Q = (\rho, \rho u, \rho E, s_{xx})$, and the Jacobian matrix is
\begin{equation}\label{eq:Jcb}
  \mathbf{J}_{e}(Q) = \left[\begin{array}{llll}
      0 & 1 & 0 & 0 \\
      -u^2 + \frac{\partial p}{\partial \rho} +\Gamma(\frac{u^2}{2}-e)& u(2-\Gamma)& \Gamma & -1 \\
	  (\Gamma(\frac{u^2}{2}-e)-e-\frac{u^2}{2}+\frac{\sigma}{\rho}+\frac{\partial p}{\partial \rho})u & -\Gamma u^2 -\frac{\sigma}{\rho}+\frac{u^2}{2} +e & (1+\Gamma)u& -u\\
    \frac{4}{3}\mu\frac{u}{\rho} & -\frac{4}{3}\mu\frac{1}{\rho}& 0 & u \\
\end{array}
\right],
\end{equation}
where $\Gamma = \frac{\Gamma_0\rho_0}{\rho} $.

@@

@@

\subsection{A relation between $\rho$ and $s_{xx}$ }\label{sec:relation}

Thanks to (\ref{eq:mt}), the equations of the density and the deviatoric stress in Eq.(\ref{eq:1d}) can be written as
  \begin{equation}\label{eq:d1}
    \frac{\partial u}{\partial x} = -\frac{1}{\rho}\frac{d\rho}{dt},
  \end{equation}
  and
  \begin{equation}\label{eq:s1}
    \frac{ds_{xx}}{dt}=\frac{4}{3}\mu\frac{\partial u}{\partial x}.
  \end{equation}

  Substituting (\ref{eq:d1}) into (\ref{eq:s1}) yields
%  We can get a relation of density and deviatoric stress,
  \begin{equation}
    \frac{ds_{xx}}{dt}=-\frac{4}{3}\mu \frac{1}{\rho}\frac{d\rho}{dt}.
\end{equation}
Integrate the above equation from the data in front of a wave to the data behind the wave and perform some simple algebraic manipulations, one can get
\begin{equation}\label{eq:rhosxx}
  s_{xx}+\frac{4}{3}\mu\text{ln}(\rho) = \text{constant}.
\end{equation}

Analyzing the formulation (\ref{eq:rhosxx}), one can find, $\frac{\partial s_{xx}}{\partial \rho}<0$. So, if the material is compressed and $\rho$ increases, $s_{xx}$ will decrease; if the material is expanded and $\rho$ decreases, $s_{xx}$ will increase. According to the compressed or expanded process of the material,  even if the initial material is in the plastic state, the material can be into a different state. With considering of the von Mises yielding condition, all cases are shown as follows:
\begin{enumerate}
  \item if $s_{xx}=\frac{2}{3}Y^{0}$, initial material reaches the elastic limit. If the material is compressed so that $\rho_{plastic}>\rho^{*}>\rho$, one can get $|s_{xx}^{*}|<\frac{2}{3}Y^{0}$, the compressed material jumps from the plastic state to the elastic state. Here $\rho$ and $s_{xx}$ mean the initial density and deviatoric stress, respectively, $\rho_{plastic} = \rho e^{\left(-\frac{Y_0}{2\mu}+\frac{3 s_{xx}}{4\mu}\right)}$, $( )^{*}$ denotes the variable $( )$ of the compressed or expanded material.
  \item if $s_{xx}=\frac{2}{3}Y^{0}$ and the material is compressed greatly so that  $\rho_{plastic}<\rho^{*}$, $s_{xx}^{*}\leq - \frac{2}{3}Y^{0}$, the compressed material will jump from the positive plastic state to the negative plastic state. Here the positive or negative plastic state means $s_{xx}=\frac{2}{3}Y^{0}$ or $s_{xx}=-\frac{2}{3}Y^{0}$, respectively.
  \item if $s_{xx}=\frac{2}{3}Y^{0}$ and  the material is expanded, $s_{xx}^{*}>\frac{2}{3}Y^{0}$, the material is still in the positive plastic state.
  \item if $s_{xx}=-\frac{2}{3}Y^{0}$ and the material is expanded so that $\rho_{plastic}<\rho^{*}<\rho$, one can get $|s_{xx}^{*}|<\frac{2}{3}Y^{0}$, the expanded material jumps from the plastic state to the elastic state.
  \item if $s_{xx}=-\frac{2}{3}Y^{0}$ and the material is expanded greatly so that  $\rho_{plastic}>\rho^{*}$, $s_{xx}^{*}\geq  \frac{2}{3}Y^{0}$, the expanded material will jump from the negative plastic state to the  positive plastic state.
  \item if $s_{xx}=-\frac{2}{3}Y^{0}$ and  the material is compressed, $s_{xx}^{*}<-\frac{2}{3}Y^{0}$, the material is still in the negative plastic state.
\end{enumerate}

@@

\noindent
\textbf{Iterations begin:}
\begin{enumerate}[Step 1]
  \item Determining the case of the wave structures:

	Given $\rho _{L(k)}^*$ and  $\rho _{R(k)}^*$ in the $k$-th  iteration step, we can use the method introduced in Section \ref{sec:deter} to determine the case of wave structures of this Riemann problem. In the  procedure for solving the  Riemann problem, the subscript $(k)$ means the variable in the $k$-th  iteration step.

@@

  After determining the structures case, we need  to solve  Cauchy stresses and velocities in regions $\mathbf{Q}^*_L$ and $\mathbf{Q}^*_R$, those are given in Section \ref{sec:functions}.

@@

Combining (\ref{shock1}) and (\ref{yield1}), we can find, in any side of the wave structures of this Riemann problem, there are six cases showed in Table \ref{tab:cases}, where capital letters ``$S$'' and ``$R$'' mean the shock and rarefaction wave, respectively; superscript letters ``$E$'' and  ``$P$'' indicate the elastic or plastic state of a wave, respectively. Otherwise, the  subscript $L$ or  $R$  are omitted for simplification.

@@

For shock waves cases, the  deviatoric stresses in $\mathbf{Q}_{L}^*$  and  $\mathbf{Q}_{R}^*$ are given as
\begin{equation}
s_{xx}(\rho) = \left\{\begin{aligned}
	  & -\frac{4}{3}\mu\text{ln}\left(\frac{\rho}{\tilde{\rho}_{L(R)}}\right)+\tilde{s}_{xxL(R)},
	\quad  &\text{for case ($S^E$)},\\
	& -\frac{2}{3}Y_0,   \quad
	&\text{for cases ( $S^P$ and $S^ES^P$)}.
  \end{aligned} \right.
  \end{equation}
(\ref{eq:shocke}) gives direct expressions for the
the pressure in the star region as
\begin{equation}
  p_{L(R)}^*=
  \frac{2t\left(c_1f(\rho_{L(R)}^*/\rho_0)+\tilde{e}_{L(R)}\right)-\left(\tilde{\sigma}_{L(R)}+{s}_{xx}(\rho_{L(R)}^*)\right)}{2tc_0-1},
\end{equation}
where $c_0 = \frac{1}{\rho_0\Gamma_0}$, $c_1 = \frac{a_0^2}{\Gamma_0}$ and $ t=\frac{\rho^*_{L(R)} \tilde{\rho}_{L(R)}}{\rho^*_{L(R)}- \tilde{\rho}_{L(R)}}$.

@@

	The initial density is  given as
\begin{equation}
\rho_{(1)}^* = \rho_R.
\end{equation}
\textbf{Iterations begin:}
\begin{enumerate}[Step 1]
  \item Determine the case of the wave structures:

	Given the value of  $\rho _{(k)}^*$ in the $k$-th iteration step, use the methods introduced in Section \ref{sec:deter} to determine the case of wave structures of this Riemann problem. Here the subscript $(k)$ means the variable in the $k$-th  iteration step.

@@

	After determining the structures case, evaluate the velocity ( or  the Cauchy stress) in  the region $\mathbf{Q}^*$ and the details are given in Section \ref{sec:functions}.

@@

\subsection{Test 1}
In this case, the material is yielding at both sides, so the solution structures has three waves with two plastic shock waves and one contact.
The initial condition is
\begin{equation}
 \left\{ \begin{aligned}
&	 \text{L: Al,}\quad  \rho = 2785 \text{kg}/\text{m}^3, \quad  u = 20\text{m}/\text{s}, \quad  p = 1.0\text{Pa}, \quad  s_{xx}=-2.0\times 10^8 \text{Pa},\\
&	 \text{R: Al,}\quad  \rho = 2785 \text{kg}/\text{m}^3, \quad  u = 0\text{m}/\text{s}, \quad  p = 1.0\text{Pa}, \quad  s_{xx}=-2.0\times 10^8 \text{Pa},\\
   \end{aligned}
 \right.
\end{equation}
It can be seen that the exact solution matches the numerical results very well in Fig.\ref{fig:case1}.
\begin{figure}[ht]
  \centering

@@

    \caption{Comparison results for Test 1 with the structures of $S^P|S^P$.  }
  \label{fig:case1}
\end{figure}
\subsection{Test 2}
Here we consider a case with yielding process at both sides, so there are five waves in the wave structures of this Riemann problem. The initial condition is
\begin{equation}
 \left\{ \begin{aligned}
	 &	 \text{L: Al,}\quad  \rho = 2785 \text{kg}/\text{m}^3, \quad  u = 800\text{m}/\text{s}, \quad  p = 1.0\text{Pa}, \quad  s_{xx}=0.0 \text{Pa},\\
&	 \text{R: Al,}\quad  \rho = 2785 \text{kg}/\text{m}^3, \quad  u = 0\text{m}/\text{s}, \quad  p = 1.0\text{Pa}, \quad  s_{xx}=0.0 \text{Pa},\\
   \end{aligned}
 \right.
\end{equation}
Shown in Fig.\ref{fig:case2}, the exact solution matches the numerical results well generally, except the under-cooling effect performed in the numerical results, but it is not considered in the designing of the exact Riemann solver.
\begin{figure}[ht]
  \centering
  \includegraphics[width= 7cm] {case2rho.pdf}
  \includegraphics[width= 7cm] {case2u.pdf}
  \includegraphics[width= 7cm] {case2p.pdf}
  \includegraphics[width= 7cm] {case2sxx.pdf}
  \caption{Comparison results for Test 2 with the structures of $S^ES^P|S^PS^E$.  }
  \label{fig:case2}
\end{figure}

\subsection{Test 3}
In this example, we test the case with two elastic rarefaction waves. In the wave structures there is one elastic rarefaction wave on each side of the contace wave. The initial condition is given as
\begin{equation}
 \left\{ \begin{aligned}
	 &	 \text{L: Al,}\quad  \rho = 2785 \text{kg}/\text{m}^3, \quad  u = -2.0\text{m}/\text{s}, \quad  p = 1.0\time 10^7\text{Pa}, \quad  s_{xx}=0.0 \text{Pa},\\
	 &	 \text{R: Al,}\quad  \rho = 2785 \text{kg}/\text{m}^3, \quad  u = 2.0\text{m}/\text{s}, \quad  p = 1.0\times 10^7 \text{Pa}, \quad  s_{xx}=0.0 \text{Pa},\\
   \end{aligned}
 \right.
\end{equation}
We can see that the results of the exact solution match the numerical results very well.
%
%j\section*{Conclusions}
\begin{figure}[ht]
  \centering

@@

    \caption{Comparison resutls for Test 7 with the structures of $R^P|R^PR^E$.  }
  \label{fig:case5}
\end{figure}
\subsection{Test 8}
In this test, we consider an example with zero initial velocities on both sides, driving by the gradient of the pressure, there are rarefaction waves produced into the higher pressure side and shock waves generated into the lower pressure side. The initial condition is given as
\begin{equation}
 \left\{ \begin{aligned}
	 &	 \text{L: Al,}\quad  \rho = 2785 \text{kg}/\text{m}^3, \quad  u = 0.0\text{m}/\text{s}, \quad  p = 1.0\times 10^{10} \text{Pa}, \quad s_{xx}= 0.0 \text{Pa},\\
	 &	 \text{R: Al,}\quad  \rho = 2785 \text{kg}/\text{m}^3, \quad  u = 0.0\text{m}/\text{s}, \quad  p = 1.0 \times 10^2 \text{Pa}, \quad  s_{xx}=0.0\text{Pa}.\\
   \end{aligned}
 \right.
\end{equation}
Shown in Fig.\ref{fig:case9}, we can see there are two shocks in the right side and two rarefaction waves on the left side.
\begin{figure}[ht]
  \centering
